Optimizing httk's 3comp2 model

### 2025-06-02 data-raw/optimizing_httk_model.Rmd
Fixing total liver flow, renal and hepatic clearance definition in 1comp_cl model functions.

pl <- plot(test_fit, use_scale_conc = FALSE,
           best_fit = FALSE, log10_C = FALSE,
           method = "L-BFGS-B")

@@

pl %>%
  filter(Chemical == "DTXSID7046627") %>%
  pull(final_plot) %>% .[[1]]

@@

pl %>%
  filter(Chemical == "DTXSID9032329") %>%
  pull(final_plot) %>% .[[1]]

>>>>

pl <- plot(test_fit, use_scale_conc = FALSE,
           best_fit = FALSE, log10_C = FALSE,
           method = "L-BFGS-B", fit_limits = 10)

@@

@@
